\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage[margin=1in,includefoot]{geometry}
\usepackage{fancyhdr}
\usepackage{mathmacros}

\fancyhead[L]{Measure Theory}
\fancyhead[R]{Alan Sun}
\fancyhead[c]{Chapter 6C: Normed Vector Spaces}
\fancyfoot{}

\fancyfoot[R]{\thepage}
\pagestyle{fancy}

\fancypagestyle{firstpage}{ \fancyfoot[L]{
    \emph{Measure, Integration, and Real Analysis by Sheldon Axler}
}}

\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{times}
\usepackage{enumitem}
\usepackage{wasysym}
\usepackage{dsfont}

\newcommand{\eps}{\varepsilon}
\theoremstyle{remark}
\newtheorem{claim}{Claim}
\newenvironment{poc}{\textit{Proof of claim:}}{\qed\\}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

\newlist{legal}{enumerate}{10}
\setlist[legal]{label*=\arabic*.}


\begin{document}
\thispagestyle{firstpage}
\begin{enumerate}[leftmargin=*]
    \item[7.] Consider the following sequence in $\ell_1$:
    \begin{gather*}
        \left(1,0,0,\ldots\right), \\
        \left(1,\frac{1}{2},0,\ldots\right), \\
        \left(1,\frac{1}{2},\frac{1}{3},0,\ldots\right).
    \end{gather*}
    The sequence is a clearly a Cauchy sequence under the $\sup_{k\in\Z^+}|a_k|$ norm, but it converges to the harmonic series which is not in $\ell_1$. Thus, $\ell_1$ with this norm is not a Banach space.
    \item[8.] Consider a Cauchy sequence, $p_1,p_2,\ldots$, in $\ell_1$, under the summation norm. Suppose that this sequence converges to some $p$. By the definition of convergence, for every $\eps > 0$, there exists $N$ such that for all $n > N$, \[
    \sum_{k=1}^\infty |p^k_n - p^k| < \eps.
    \]
    It follows that 
    \begin{align*}
        \sum_{k=1}^\infty |p^k| &\leq \sum_{k=1}^\infty |p^k_n - p^k| + \sum_{k=1}^\infty |p^k_n|, \\
        &< \eps + \sum_{k=1}^\infty |p^k_n|.
    \end{align*}
    This last expression is finite since $p_n \in \ell_1$. Thus, it follows that $\ell_1$ with the summation norm is complete which implies that it is a Banach space.
    \item[9.] Consider the sequence of functions \[
    f_k(x) = \frac{1}{1+e^{-k(x-1)}}.
    \]
    Each of these functions is continuous and is a Cauchy sequence under the norm $\int_0^1|f|$. However, the sequence of functions converge to 
    \[
        f(x) = \begin{cases}1 &\text{if}\,x\geq 0.5 \\ 0 &\text{o/w}.\end{cases}
    \]
    which is not in $C([0,1])$.
    \item[12.] Since $W$ is a subspace, $0 \in W$. And for any $w \in W, w \in \overline{W}$. Now, suppose that $a, b \in \overline{W}$. We show that $a + b \in \overline{W}$. By assumption, for every $\eps > 0$, there exists $a' \in B(a,\eps/2) \cap W$ and $b' \in B(b,\eps/2) \cap W$. Since $W$ is a subspace, it must be that $a' + b' \in W$. Now,
    \begin{align*}
        \lVert (a + b) - (a' + b') \rVert &= \lVert (a - a') + (b - b') \rVert, \\
        &\leq \lVert a - a'\rVert + \lVert b - b' \rVert, \\
        &< \frac{\eps}{2} + \frac{\eps}{2} = \eps.
    \end{align*}
    Thus, $a' + b' \in B(a + b, \eps) \cap W$. So, $\overline{W}$ is closed under addition. 

    For $\alpha \in \F, w \in W$, $\eps > 0$, let $w' \in B(w, \eps/|\alpha|) \cap W$. Then, it follows that $\frac{w'}{\alpha} \in W$ since $W$ is a subspace. Moreover,
    \begin{align*}
        \lVert \alpha w - w' \rVert &= \left\lVert \alpha\left(w - \frac{w'}{\alpha}\right)\right\rVert, \\
        &= |\alpha|\left\lVert w - \frac{w'}{\alpha}\right\rVert < |\alpha|\cdot \frac{\eps}{|\alpha|} = \eps.
    \end{align*}

    
    \item[16.] \begin{enumerate}
        \item For $\eps > 0$, there exists $\alpha \in \F, \alpha \neq 0$ such that $|| \alpha f || = 1$ when $|| f || < 1$. This also implies that $|\alpha| > 1$. Thus, 
        \begin{align*}
            \lVert T(\alpha f) \rVert &= \lVert \alpha \cdot Tf \rVert = |\alpha|\cdot \lVert Tf \rVert > \lVert  Tf \rVert.
        \end{align*}
        This implies that 
        \[
        \sup\{|| Tf || : f\in V, ||f || < 1\} \leq \sup \{ || Tf || : f \in V ||f || \leq 1\}.
        \]
        It remains to show the inequality in the other direction. By way of contradiction, suppose that there exists $f \in V, ||f || = 1$ and $\eps > 0$ such that for all $g \in V$ where $||g|| < 1$ and $||Tg || + \eps < ||Tf||$. 

        Consider first the case where $||Tf||$ is infinite. Since $||g || < 1$, there must exist some $g' \in V$ where $||g' || < 1$ such that $|| g + g' || = 1$. Then, by assumption,
        \[
        \infty = || T (g + g') || \leq || T g || + || T g' ||.
        \]
        This implies that either $|| Tg ||$ or $|| T g'||$ is infinite which is a contradiction. Now, consider the case where $|| Tf || < \infty$. This implies that $T$ is a bounded linear map which means that $T$ is continuous. Thus, for any $\eps > 0$, there exists $\delta > 0$ such that for all $|| f -g || < \delta$, $|| Tf - Tg || < \eps$. This contradicts the assumption and proves the inequality in the other direction.

        \item 

        
    \end{enumerate}
    \item[18.] That (a $\Rightarrow$ b) follows immediately from the fact that every bounded linear map is continuous.
\end{enumerate}
\end{document}
